Continuous Deductive Reasoning over Streamed RDF Data

### 2015-07-10 content/abstract.tex
Added abstract

Continuous Datalog semantics

CoDeR Logical Model (minimal algebra and stream data model) for Continuous Deductive Reasoning

Physical Model and Windowed Rete Algorithm

R4 (\& Squall)

Evaluation (against Sparkwave \cite{sparkwave} and CQELS)

>>>>

In this paper, we introduce Continuous Datalog, an extension of
conventional Datalog that adds the concept of streams of
temporally-annotated facts to conventional Datalog and defines the
notion of entailment over a windowed stream. We go on to define CoDeR,
an abstract model for continuous deductive reasoning that provides
both a data stream model based on Continuous Datalog and a minimal
algebra for expressing queries and programs.  Finally, we describe the
R4 stream reasoner, which implements the CoDeR model as a Rete-based
dataflow network and provide a brief comparative evaluation of R4
against ETALIS and Sparkwave.
